Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-11 manuscript.Rmd
Attempting full analysis from scratch

processdata <- 0   # running all analyses from scratch takes about 6 hours
buildfigures <- 0

# currently activating the LSA package seems to crash the script on github
# now trying a direct call to the Cosine function with the package unactivated

# install.packages("LSAfun")

>>>>

processdata <- 1   # running all analyses from scratch takes about 6 hours
buildfigures <- 1
